---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BSOLwaitinglist

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of BSOLwaitinglist is wrap some of the functions in the 2025 planning, and related modelling processes, into a single documented package that calls others and allows others to produce waiting list projections and simulations.

Work in progress, not all transfered, tested or built yet.

## Installation

You can install the development version of BSOLwaitinglist like so:

```{r install, echo=TRUE, eval=FALSE}
# install.packages("remotes")
remotes::install_github("Birmingham-and-Solihull-ICS/BSOLwaitinglist", build_vignettes = TRUE)
```

